---
title       : Developing Data Products Homework 4
subtitle    : Homework presentation using slidify
author      : Philip To
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r setup, include=FALSE, fig.width = 10, fig.height = 4, fig.align = "center"} 
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warnings = FALSE) 
library(ggplot2)
library(lubridate)
library(reshape2)

```

## Introduction

* This web app was developed using R Shiny package and hosted online on shinyapps.io.
* To get access to the web app, please visit the following: 
https://philipto.shinyapps.io/hw4_app/

--- .class #id 


## Features

* The web app allows the user to perform the following functions:

(1) Change the title of the chart; 

(2) Select which card to plot the CPU measurements; 

(3) Change the position of the legend; 

(4) Zoom into selected data points for better view.

(5) Computes the average CPU measurement for the selected data range.

---

## Charts With No Interactivities

This is an example of static chart.  It does not provide any interactivity.  The usefulness of such chart is very limited.

```{r, echo=FALSE, results="hide"} 
  
  tmp_df <- read.csv("Avg_CPU.csv")
    tmp_df$Time <- parse_date_time(tmp_df$Time,c( "mdyHMS", "ymdHMS"), tz = "EST")

    tmp_df2 <- melt(tmp_df, measure.vars=names(tmp_df)[2:ncol(tmp_df)])
    names(tmp_df2)[2] <- "CPU"
    
    main_title <- "CPU Measurement"
    
    ggplot(data=tmp_df2,aes_string(x = "Time", y = "value")) + geom_line(aes_string(color="CPU")) + 
      #scale_y_continuous(name="CPU",labels = scales::comma) +
      ggtitle(main_title) + theme(
        axis.text.y = element_text(colour = "black"),
        axis.title=element_text(face="bold",colour="brown"),
        plot.title = element_text(color="brown", face="bold", size=18, hjust=0.5),
        legend.position="top",
        legend.title = element_text(color = "black"),
        legend.text =  element_text(color = "black")
      )

    
   

```

---

## Magnified View Possible On The Web App

* This is an example of a zoomed in chart after the user selected a subset of data points.

```{r, echo=FALSE, results="hide"} 
  
  tmp_df <- read.csv("Avg_CPU2.csv")
    tmp_df$Time <- parse_date_time(tmp_df$Time,c( "mdyHMS", "ymdHMS"), tz = "EST")

    tmp_df2 <- melt(tmp_df, measure.vars=names(tmp_df)[2:ncol(tmp_df)])
    names(tmp_df2)[2] <- "CPU"
    
    main_title <- "Magnified View"
    
    ggplot(data=tmp_df2,aes_string(x = "Time", y = "value")) + geom_line(aes_string(color="CPU")) + 
      #scale_y_continuous(name="CPU",labels = scales::comma) +
      ggtitle(main_title) + theme(
        axis.text.y = element_text(colour = "black"),
        axis.title=element_text(face="bold",colour="brown"),
        plot.title = element_text(color="brown", face="bold", size=18, hjust=0.5),
        legend.position="top",
        legend.title = element_text(color = "black"),
        legend.text =  element_text(color = "black")
      )

    
   

```





